### 2022-06-16 paper.tex
initial

\documentclass{article}
%\documentclass[twocolumn]{article}%
\usepackage[utf8]{inputenc}%
\usepackage{standalone}%
\usepackage{amsmath}%
\usepackage{amsthm}%
\usepackage{amssymb}%
\usepackage{hyperref}%
\usepackage{xcolor}%
\usepackage{tabularx}%
\usepackage{listings}%
\lstdefinestyle{b}{basicstyle=\tiny\ttfamily}
\lstset{
  showspaces=false,
  showstringspaces=false
  }

% Add your keywords here, and have this in a separate file
% and include it in your preamble
\lstset{emph={%
    function, uint256, public, mapping,contract,bytes,bool, if, for,
    field, private, def, import, assert, require, zksnarkverify %
},emphstyle={\color{blue}\bfseries}%
}

%\definecolor{keywords}{HTML}{8A4A0B}
%
%\definecolor{background}{HTML}{EEEEEE}
%
%\lstset{language=[LaTeX]Tex,
%    keywordstyle=\color{keywords},
%    keywordstyle=[2]\color{red},
%    keywordstyle=[3]\color{orange},
%    basicstyle=\normalfont\ttfamily,
%    showstringspaces=false,
%    frameround=ftff,
%    frame=lines,
%    morekeywords={RequirePackage,ProvidesPackage},
%    keywords=[2]{Some,Other,Keywords},
%    keywords=[3]{and,another,test},
%    backgroundcolor=\color{background}
%}

\newcommand{\khk}{$P$}
\newcommand{\khkp}{$K^{-1}[\text{HK}]$}
\newcommand{\identity}{\textit{Identity}}
%\newcommand{\kid}{$K[\text{\identity}]$}
\newcommand{\kid}{$K$}
\newcommand{\todo}[1]{\fbox{\parbox{\linewidth}{\textcolor{red}{#1}}}}
\newcommand{\iv}{$IV(\text{\identity})$}
\newcommand{\sigid}{$K^{-1}[CA](K[Identity])$}
\newtheorem{problem}{Problem}
\newenvironment{solution}
  {\emph{Solution:}}
  {\hfill $\square$}
\newcommand{\pbc}{\textit{PeopleBC}}

\title{Proof of Identity}
\author{Albert Vučinović, University North}
\begin{document}
\maketitle
\section{Notation}
\begin{tabular}{p{0.36\linewidth}|p{0.55\linewidth}}
	\kid &  State CA certified public key of e.g. eID\\
	$K(value)$ & $value$ encrypted with the public key $K$. \\
	$\kid^{-1}$ & Private key corresponding to the public key $K$. \\
  \khk & Person key, used to access PeopleBC as an unknown Person. \\
  $H$ & SHA256 \\
\end{tabular}

\newpage
\section{Registering \khk{} (Person key)}
\begin{enumerate}
  \item Use \kid{} to sign "PeopleBC", $K_1 = \kid^{-1}("registerK")$.
  \begin{enumerate}
    \item Entities who know \kid{} (e.g. CA that issued it) can know that the Person is using PeopleBC, and what identification document the Person is using.
  \end{enumerate}
  \item Register \kid{} on \pbc, by calling 
    $$registerK(Pin, K_1, proofPinOwnsK)$$.
  \item Register \khk{} on \pbc, by calling 
    $$registerP(PinK, PinKP, proof)$$
  where:
    \begin{enumerate}
      \item $K_2=\kid^{-1}("registerP")$
      \item $PinK=H(Pin,K_2)$
      \item $P_1 = \khk^{-1}("registerP")$
      \item $PinKP=H(Pin, K_2, P_1)$
    \end{enumerate}
\end{enumerate}

\newpage
\section{On chain code}
\begin{lstlisting}[language=C, frame=single, style=b]
//pseudo Solidity
//Key is eID private key, or PrivateeIDKey("")
//PersonKey is Blockchain key used by a Person
contract IdentitiesManager {
  //all the mappings are mappings where uint256 is a hash!
  mapping(uint256 => uint256) public PinKUsed;
  mapping(uint256 => uint256) public PinKPUsed;
  mapping(uint256 => uint256) public PinKPLastConfirmed;
  mapping(uint256 => bool) public PInvalid;
  mapping(uint256 => bool) public KInvalid;
  //TODO:CA fields!

  //K_1=K_1("registerK")
  //Pin=H(Pin)
  function registerK public(
    uint256 Pin,
    uint256 K_1,
    bytes proofPinOwnsK
  ){
    uint256 previousKey = PinKUsed[Pin];
    if(previouseKey == K_1)
      return;
    bool isOwner = zksnarkverify(VK, [
        PIN, 
        K_1
      ],
      proofPINOwnsK);
    if(isOwner && ! KInvalid[K_1]){
      if(previousKey!=0)
        KInvalid[previousKey]=true;
      PinKUsed[Pin]=K_1;
    }
  }

  //PinK=H(Pin, K_1("registerP")) which is != H(Pin, K_1("registerK"))
  //PinK can not be connected to Pin, unless one knows K_1
  function registerP public(
    uint256 PinK,
    uint256 PinKP,
    bytes proof
  ){
    uint256 previousKey = PinKPUsed[PinK]
    if(previousKey == PinK)
      return; //already registered

    //zkp(
      //K!invalid
        //?Need KInvalid to be Zero Knowledge Set (ZKS), and to get roots
      //CA!invalid
      //CA -> K -> Pin
      //PinK=H(Pin, K_1("registerP"))
      //PinKP=H(Pin, K_1("registerP"), P_1("registerP"))
    //)
    bool ok = zksnarkverify(VK, [
    ], proof);

    if(ok && ! PInvalid[PinKP]){
      if(previousKey != 0)
        PInvalid[previousKey]=true;
      PinKPUsed[PinK]=PinKP;
      PinKPLastConfirmed[PinK]=block.number;
    }

  }

}

contract PersonAccount{
}
\end{lstlisting}

\newpage
\section{zkp code}
\begin{lstlisting}[language=C, frame=single, style=b]
//pseudo zokrates zk-SNARK
import "hashes/sha256/512bitPacked" as sha256packed
import "ecc/babyjubjubParams.code" as context
import "ecc/proofOfOwnership.code" as proofOfOwnership

def proofPINOwnsK(
  field[2] PINHash,
  field[2] K_1Hash,
  field[2]

  private field[?] CACert){
}

def proof_of_being_a_person(
  //publically known arguments
  field[2] PINKeyUsedHash,
  field[2] PINKeyPersonKeyIssuedHash,
  field[2] PersonKeyInvalidHash,
  field[2] KeyInvalidHash,

  //BC state
  field BC_PINUsed,//BC State
  field BC_PINKeyUsed,//BC State
  field BC_PINKeyPersonKeyIssued,//BC State
  field BC_PersonKeyInvalid,//BC State
  field BC_KeyInvalid,//BC State
  ?field BC_private_key_challenge?

  //CA keys!
  field[?][?] CAKeys,//? BC State
  ...

  //private data
  //15360 bit RSA key is equivalent to 256-bit symmetric keys
  //2048 bit RSA key is equivalent to 112 bit symmetric keys
  //eID has 2048 bit RSA
  private field PIN,//max 254 bits, using only 128 = 16 bytes
  private field K_private_bc_new,//ECC private key
  private field[?] K_new,//public RSA key from eID
  private field[?] K_1_new,//private RSA key from eID, actually signed message
  //K_1_new("PeopleBC person proof")
  private field K_private_bc_old,//ECC private key, old
  private field[?] K_1_old)//K_1_old("PeopleBC person proof")?
  //?private field[2] K_bc_new,//ECC public key ?no need for key pair verification?
  //?private field[2] K_bc_old,//ECC public key ?no need for key pair verification
  private field[?] CAcert,
  private field CAindex
{
  //actual checking code here
  field[2] hash_PIN = sha256packed([0,0,0,PIN])
  assert(hash_PIN == PINHash);//proving that we know the real PIN, unimportant

  //proving ownership of newly registered key, 
  //no real need to prove ownership of bc key
  //we actually need to prove ownereship of K_1_new, 
  //and its connection to PIN via CA
  context=context()//babyjubjubParams context
  proofOfOwnership(K_bc_new, K_private_bc_new, context)==1

  //prove that you own the K_new
  //pseudo
  RSADecrypt(K_new, K_1_new) == "PeopleBC Person Proof";//?+BC_private_key_challenge;

  //proove that Key is connected to CA
  //pseudo
  checkCASignature(CAKey[CAindex], CACert, K_new) == 1;

  //proove that K_new is PIN certificate
  //pseudo
  extractPIN(CACert)==PIN;

  //end

  //end..
}
\end{lstlisting}
\newpage
\section{Problems}
\begin{problem}
  The rate of adding identities, the problem being frequent changes of Merkle Tree Roots, and how long it takes to generate zkp proof, and block generation time.
\end{problem}
\begin{problem}
\label{prob:bigsteal}
  Someone stole $K^{-1}$ before we registered on \pbc.
  The Thief registered $K$ and $P$, and who knows what else.
\end{problem}
\begin{solution}
\end{solution}
\begin{problem}
  Someone stole $K^{-1}$ after we registered on \pbc.
\end{problem}
\begin{problem}
Trying to use unregistered Key.
\end{problem}
\begin{solution}
\end{solution}
\begin{problem}
Trying to register the same PIN with multiple Keys (e.g. two physical ids).
\end{problem}
\begin{problem}
\label{prob:chain}
  Using $P$ without checking the whole $CA\rightarrow K\rightarrow P$ chain.
  \begin{itemize}
    \item Using $P$ to register as a mining key.
    \item Invalidating $P$.
    \item Using $P_{new}$ as a mining key.
  \end{itemize}
\end{problem}
\begin{solution}
  Look at the solution to Problem \ref{prob:miningKey}.

  The Mining Registry can accept new $P$s after an expiration period (which can also be e.g. 1 day).
\end{solution}
\begin{problem}
\label{prob:miningKey}
  A combination of Problem \ref{prob:bigsteal} and Problem \ref{prob:chain}.
  Someone steals $K$, registeres $P$ and registeres $P$ for mining.
  The problem is bigger, because we can't invalidate $P$ if we don't know which $P$ it is.
\end{problem}
\begin{solution}
  We make $P$ renewable. We write the last block number it was renewed on to the blockchain.
  Mining Registry can choose to accept P which is not older than some time period (for the Registry a good period would seem to be 1 day).
  When paying the miners, the Registry also requires proof of $P$'s age.

  $K$ is easely invalidated, because there is an explicit $PIN \rightarrow K^{-1}$ mapping on the blockchain, so it doesn't need to be renewable in the sence to proove it is still valid.
\end{solution}
\begin{problem}
  Only $P$ compromised.
\end{problem}
\end{document}

### 2022-06-17 startDocker.sh
docker container for building pdf

@@ -1,0 +1,1 @@
+docker run --rm -it -v "$(pwd)":/source schickling/latex

### 2022-06-26 paper.tex
Update paper.tex
none
K_id, K_p instead of K, P; explanations; notation

@@
 
-\newcommand{\khk}{$P$}
+\newcommand{\khk}{K_{P}}
 \newcommand{\khkp}{$K^{-1}[\text{HK}]$}
-\newcommand{\identity}{\textit{Identity}}
-%\newcommand{\kid}{$K[\text{\identity}]$}
-\newcommand{\kid}{$K$}
+\newcommand{\kid}{K_{ID}}
+%\newcommand{\kid}{$K$}
 \newcommand{\todo}[1]{\fbox{\parbox{\linewidth}{\textcolor{red}{#1}}}}
@@
   {\hfill $\square$}
-\newcommand{\pbc}{\textit{PeopleBC}}
+\newcommand{\pbc}{\textit{Identity Blockchain}}
 
 \title{Proof of Identity}
-\author{Albert Vučinović, University North}
+\author{
+Albert Vučinović, University North\\
+Miroslav Jerković, University of Zagreb
+}
 \begin{document}
@@
 \begin{tabular}{p{0.36\linewidth}|p{0.55\linewidth}}
-	\kid &  State CA certified public key of e.g. eID\\
-	$K(value)$ & $value$ encrypted with the public key $K$. \\
-	$\kid^{-1}$ & Private key corresponding to the public key $K$. \\
-  \khk & Person key, used to access PeopleBC as an unknown Person. \\
-  $H$ & SHA256 \\
+  $(K, K^{-1})$ & A pair of public $K$ and the corresponding private key $K^{-1}$. \\
+	$K(value)$ & $value$ encrypted with a public key $K$. \\
+	$K^{-1}(value)$ & $value$ encrypted with a private key $K^{-1}$. \\
+  $H$ & Hash function, e.g. some zksnark friedly one \\
+	$\kid$ &  State CA certified public key of e.g. eID\\
+  $\khk$ & Person key, public key used to access \pbc{} as an unknown Person. \\
+  $Nin$ & A personal National Identification Number issued by state.
 \end{tabular}
 
+Sometimes we write $K$ for $(K, K^{-1})$.
+
 \newpage
-\section{Registering \khk{} (Person key)}
+\section{Registering $\khk$ (Person key)}
 \begin{enumerate}
-  \item Use \kid{} to sign "PeopleBC", $K_1 = \kid^{-1}("registerK")$.
-  \begin{enumerate}
-    \item Entities who know \kid{} (e.g. CA that issued it) can know that the Person is using PeopleBC, and what identification document the Person is using.
-  \end{enumerate}
-  \item Register \kid{} on \pbc, by calling 
-    $$registerK(Pin, K_1, proofPinOwnsK)$$.
-  \item Register \khk{} on \pbc, by calling 
-    $$registerP(PinK, PinKP, proof)$$
+  \item Register $\kid$ on \pbc, by calling 
+    $$register\kid(Nin, \kid^{-1}("register\kid"), proofNinOwnsK).$$
+
+    The Person tells the \pbc{} what personal identification document will they be using.
+
+    What is the meaning behind $register\kid$ function?
+    \begin{itemize}
+      \item Sybil resistance. To prevent a Person from registering more than one $\khk$ using different identification documents, which are issued for the same $Nin$.
+      \item Loss of $\kid$. If a Person looses previously registered $\kid$ (e.g. by loosing the eID), they can register a new one.
+      \item Identity theft damage control. If a Person overwrites the previous $\kid$ with a new one, the identity thief will loose access to services that check the whole identity chain.
+    \end{itemize}
+
+    Entities who know $\kid$ (e.g. CA that issued it) can know that the Person is using \pbc{}, and what identification document the Person is using.
+
+  \item Register $\khk$ on \pbc, by calling 
+    $$register\khk(Nin\kid, Nin\kid\khk, proof)$$
   where:
     \begin{enumerate}
-      \item $K_2=\kid^{-1}("registerP")$
-      \item $PinK=H(Pin,K_2)$
-      \item $P_1 = \khk^{-1}("registerP")$
-      \item $PinKP=H(Pin, K_2, P_1)$
+      \item $Nin\kid=H(Nin,\kid^{-1}("register\khk"))$
+      \item $Nin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$
     \end{enumerate}

### 2022-06-26 paper.tex
registerKid notation

@@
 \newpage
-\section{Registering $\khk$ (Person key)}
+\section{Registering $\khk$}
 \begin{enumerate}
   \item Register $\kid$ on \pbc, by calling 
-    $$register\kid(Nin, \kid^{-1}("register\kid"), proofNinOwnsK).$$
+    $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsK).$$
 
@@
 
+    The reasoning behind the choice of arguments for the $register\kid$ function:
+
+    If we used:
+    \begin{itemize}
+      \item $register\kid(H(Nin, \kid^{-1}("register\kid")), proofNinOwnsK)$
+
+        TODO: explain
+      \item $register\kid(Nin, \kid^{-1}("register\kid"), proofNinOwnsK)$
+
+        TODO: explain
+    \end{itemize}
+
   \item Register $\khk$ on \pbc, by calling 
@@
     \end{enumerate}
+
+  The Person registers a $\khk$, which is a unique public key tied to the Person on the \pbc{}.
+  What is the meaning behind $register\khk$ function?
+  \begin{itemize}
+    \item Sybil resistance. $\khk$ is the only such key that is tied to the Person with the samo $Nin$.
+      By design, the Person can not own two valid $\khk$s at the same time.
+
+      TODO: Explanation/proof.
+    \item Anonimity.
+Someone with a database of all the $\kid$ public keys or/and the database of all the $\khk$ public keys, shouldn't be able to determine which $Nin$, $\kid$ or $\khk$ was used, from the function call.
+
+    TODO: Explanation/proof.
+
+    The assumption is that the CA doesn't have access to $\kid^{-1}$, i.e. that $\kid$ is generated safely on the eID.
+  \end{itemize}
+  The reasoning behind the choice of arguments for the $register\khk$ function:
+
+  TODO: 
 \end{enumerate}
@@
   //all the mappings are mappings where uint256 is a hash!
-  mapping(uint256 => uint256) public PinKUsed;
-  mapping(uint256 => uint256) public PinKPUsed;
-  mapping(uint256 => uint256) public PinKPLastConfirmed;
-  mapping(uint256 => bool) public PInvalid;
-  mapping(uint256 => bool) public KInvalid;
+  mapping(uint256 => uint256) public NinKidUsed;
+  mapping(uint256 => uint256) public NinKidKpUsed;
+  mapping(uint256 => uint256) public NinKidKpLastConfirmed;
+  mapping(uint256 => bool) public KpInvalid;
+  mapping(uint256 => bool) public KidInvalid;
   //TODO:CA fields!
 
-  //K_1=K_1("registerK")
-  //Pin=H(Pin)
-  function registerK public(
-    uint256 Pin,
-    uint256 K_1,
-    bytes proofPinOwnsK
+  //vKid=KidPrivate("registerKid")
+  //Nin=H(Nin)
+  function registerKid public(
+    uint256 Nin,
+    uint256 vKid,
+    bytes proofNinOwnsKid
   ){
-    uint256 previousKey = PinKUsed[Pin];
-    if(previouseKey == K_1)
+    uint256 previousKey = NinKidUsed[Nin];
+    if(previousKey == vKid)
       return;
     bool isOwner = zksnarkverify(VK, [
-        PIN, 
-        K_1
+        Nin, 
+        vKid
       ],
-      proofPINOwnsK);
-    if(isOwner && ! KInvalid[K_1]){
+      proofPINOwnsKid);
+    if(isOwner && ! KidInvalid[vKid]){
       if(previousKey!=0)
-        KInvalid[previousKey]=true;
-      PinKUsed[Pin]=K_1;
+        KidInvalid[previousKey]=true;
+      NinKidUsed[Nin]=vKid;
     }

### 2022-06-26 paper.tex
enough for today

@@
 //pseudo Solidity
-//Key is eID private key, or PrivateeIDKey("")
-//PersonKey is Blockchain key used by a Person
 contract IdentitiesManager {
@@
 
+  //hNin=H(Nin)
   //vKid=KidPrivate("registerKid")
-  //Nin=H(Nin)
   function registerKid public(
-    uint256 Nin,
+    uint256 hNin,
     uint256 vKid,
@@
   ){
-    uint256 previousKey = NinKidUsed[Nin];
+    uint256 previousKey = NinKidUsed[hNin];
     if(previousKey == vKid)
@@
     bool isOwner = zksnarkverify(VK, [
-        Nin, 
+        hNin, 
         vKid
@@
         KidInvalid[previousKey]=true;
-      NinKidUsed[Nin]=vKid;
+      NinKidUsed[hNin]=vKid;
     }
@@
 
-  //PinK=H(Pin, K_1("registerP")) which is != H(Pin, K_1("registerK"))
-  //PinK can not be connected to Pin, unless one knows K_1
-  function registerP public(
-    uint256 PinK,
-    uint256 PinKP,
+  //look into the paper.pdf for meaning of args
+  function registerKp public(
+    uint256 NinKid,
+    uint256 NinKidKp,
     bytes proof
   ){
-    uint256 previousKey = PinKPUsed[PinK]
-    if(previousKey == PinK)
+    uint256 previousKey = NinKidKpUsed[NinKid]
+    if(previousKey == NinKid)
       return; //already registered
@@
       //CA!invalid
-      //CA -> K -> Pin
-      //PinK=H(Pin, K_1("registerP"))
-      //PinKP=H(Pin, K_1("registerP"), P_1("registerP"))
+      //CA -> K -> Nin
+      //NinKid=H(Nin, KidPrivate("registerP"))
+      //NinKidKp=H(Nin, KidPrivate("registerP"), KpPrivate("registerP"))
     //)
     bool ok = zksnarkverify(VK, [
+      NinKid,
+      NinKidKp
     ], proof);
 
-    if(ok && ! PInvalid[PinKP]){
+    if(ok && ! PInvalid[NinKidKp]){
       if(previousKey != 0)
         PInvalid[previousKey]=true;
-      PinKPUsed[PinK]=PinKP;
-      PinKPLastConfirmed[PinK]=block.number;
+      NinKidKpUsed[NinKid]=NinKidKp;
+      NinKidKpLastConfirmed[NinKid]=block.number;
     }

### 2022-06-28 paper.tex
updated pages 1-3, 6

--- 2022-06-26 paper.tex
@@
 \usepackage{listings}%
-\lstdefinestyle{b}{basicstyle=\tiny\ttfamily}
-\lstset{
-  showspaces=false,
-  showstringspaces=false
+\usepackage{colortbl}
+\usepackage{enumitem}
+
+\usepackage{listings, xcolor}
+
+\definecolor{verylightgray}{rgb}{.97,.97,.97}
+
+\lstdefinelanguage{Solidity}{
+	keywords=[1]{anonymous, assembly, assert, balance, break, call, callcode, case, catch, class, constant, continue, constructor, contract, debugger, default, delegatecall, delete, do, else, emit, event, experimental, export, external, false, finally, for, function, gas, if, implements, import, in, indexed, instanceof, interface, internal, is, length, library, log0, log1, log2, log3, log4, memory, modifier, new, payable, pragma, private, protected, public, pure, push, require, return, returns, revert, selfdestruct, send, solidity, storage, struct, suicide, super, switch, then, this, throw, transfer, true, try, typeof, using, value, view, while, with, addmod, ecrecover, keccak256, mulmod, ripemd160, sha256, sha3}, % generic keywords including crypto operations
+	keywordstyle=[1]\color{blue}\bfseries,
+	keywords=[2]{address, bool, byte, bytes, bytes1, bytes2, bytes3, bytes4, bytes5, bytes6, bytes7, bytes8, bytes9, bytes10, bytes11, bytes12, bytes13, bytes14, bytes15, bytes16, bytes17, bytes18, bytes19, bytes20, bytes21, bytes22, bytes23, bytes24, bytes25, bytes26, bytes27, bytes28, bytes29, bytes30, bytes31, bytes32, enum, int, int8, int16, int24, int32, int40, int48, int56, int64, int72, int80, int88, int96, int104, int112, int120, int128, int136, int144, int152, int160, int168, int176, int184, int192, int200, int208, int216, int224, int232, int240, int248, int256, mapping, string, uint, uint8, uint16, uint24, uint32, uint40, uint48, uint56, uint64, uint72, uint80, uint88, uint96, uint104, uint112, uint120, uint128, uint136, uint144, uint152, uint160, uint168, uint176, uint184, uint192, uint200, uint208, uint216, uint224, uint232, uint240, uint248, uint256, var, void, ether, finney, szabo, wei, days, hours, minutes, seconds, weeks, years},	% types; money and time units
+	keywordstyle=[2]\color{teal}\bfseries,
+	keywords=[3]{block, blockhash, coinbase, difficulty, gaslimit, number, timestamp, msg, data, gas, sender, sig, value, now, tx, gasprice, origin},	% environment variables
+	keywordstyle=[3]\color{violet}\bfseries,
+	identifierstyle=\color{black},
+	sensitive=false,
+	comment=[l]{//},
+	morecomment=[s]{/*}{*/},
+	commentstyle=\color{gray}\ttfamily,
+	stringstyle=\color{red}\ttfamily,
+	morestring=[b]',
+	morestring=[b]"
 }
 
-% Add your keywords here, and have this in a separate file
-% and include it in your preamble
-\lstset{emph={%
-    function, uint256, public, mapping,contract,bytes,bool, if, for,
-    field, private, def, import, assert, require, zksnarkverify %
-},emphstyle={\color{blue}\bfseries}%
+\lstset{
+	language=Solidity,
+	backgroundcolor=\color{verylightgray},
+	extendedchars=true,
+	basicstyle=\footnotesize\ttfamily,
+	showstringspaces=false,
+	showspaces=false,
+	numbers=left,
+	numberstyle=\footnotesize,
+	numbersep=9pt,
+	tabsize=2,
+	breaklines=true,
+	showtabs=false,
+	captionpos=b
 }
-
-%\definecolor{keywords}{HTML}{8A4A0B}
-%
-%\definecolor{background}{HTML}{EEEEEE}
-%
-%\lstset{language=[LaTeX]Tex,
-%    keywordstyle=\color{keywords},
-%    keywordstyle=[2]\color{red},
-%    keywordstyle=[3]\color{orange},
-%    basicstyle=\normalfont\ttfamily,
-%    showstringspaces=false,
-%    frameround=ftff,
-%    frame=lines,
-%    morekeywords={RequirePackage,ProvidesPackage},
-%    keywords=[2]{Some,Other,Keywords},
-%    keywords=[3]{and,another,test},
-%    backgroundcolor=\color{background}
-%}
 
@@
 
-\title{Proof of Identity}
+\title{Identity Blockchain - Proof of Identity}
 \author{
@@
 \maketitle
+
+\begin{abstract}
+$\pbc$ uses state-certified electronic identities (eIDs) to create blockchain identities and a consensus protocol called Proof of Identity (PoI).
+PoI is "green" and enables many applications that are impossible to implement without verified identity on the blockchain, e.g., direct democracy and universal basic income, encrypted messaging, etc.
+$\pbc$ preserves identity anonymity by using zk-SNARKs and an anonymization protocol for identity onboarding.
+\end{abstract}
+
+\section{Introduction}
+TODO
+
 \section{Notation}
-\begin{tabular}{p{0.36\linewidth}|p{0.55\linewidth}}
-  $(K, K^{-1})$ & A pair of public $K$ and the corresponding private key $K^{-1}$. \\
-	$K(value)$ & $value$ encrypted with a public key $K$. \\
-	$K^{-1}(value)$ & $value$ encrypted with a private key $K^{-1}$. \\
-  $H$ & Hash function, e.g. some zksnark friedly one \\
-	$\kid$ &  State CA certified public key of e.g. eID\\
-  $\khk$ & Person key, public key used to access \pbc{} as an unknown Person. \\
-  $Nin$ & A personal National Identification Number issued by state.
+\vspace{10px}
+ \arrayrulecolor{gray}
+\begin{tabular}{p{0.16\linewidth}| p{0.84\linewidth}}
+  $(K, K^{-1})$ & \ \ Pair of public key $K$ and the corresponding private key $K^{-1}$ \\[3px]
+	$K(value)$ & \ \ String $value$ encrypted with a public key $K$ \\[3px]
+	$K^{-1}(value)$ & \ \ String $value$ encrypted with a private key $K^{-1}$ \\[3px]
+  $H$ & \ \ zk-SNARK-friendly hash function \\[5px]
+ \hline \\
+   $Nin$ & \ \ Unique state-issued personal \textit{National Identification Number}\\[3px]
+   $CA$ & \ \ Certificate Authority \\[3px]
+   $eID$ & \ \ Electronic identification document \\[3px]
+	$\kid$ & \ \ CA-certified public key of eID\\[3px]
+  $\khk$ & \ \ Person key, unique public key used to access \pbc{}
+
 \end{tabular}
+
+\vspace{15px}
 
@@
 \newpage
-\section{Registering $\khk$ (Person key)}
-\begin{enumerate}
-  \item Register $\kid$ on \pbc, by calling 
-    $$register\kid(Nin, \kid^{-1}("register\kid"), proofNinOwnsK).$$
+\section{Registering $\kid$}
+Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsKid).$$
+\begin{enumerate}[leftmargin=0cm]
+\item[] \underline{Pseudo-solidity code}
 
-    The Person tells the \pbc{} what personal identification document will they be using.
+\hfill\begin{minipage}{\dimexpr\textwidth-20px}
+\begin{lstlisting}[language=Solidity]
+  mapping(uint256 => uint256) public ninKidUsed;
+  mapping(uint256 => bool) public kidInvalid;
 
-    What is the meaning behind $register\kid$ function?
+  function registerKid(
+    uint256 hNin, // hNin = H(Nin)
+    uint256 vKid, // vKid = KidPrivate("registerKid")
+    bytes proofNinOwnsKid
+  ) public {
+    uint256 previousKey = ninKidUsed[hNin];
+    if (previousKey == vKid) return; // already registered
+    bool isOwner = zksnarkverify(VK, [hNin, vKid], proofNinOwnsKid); // VK = verification key
+    if (isOwner && !kidInvalid[vKid]) {
+      if (previousKey != 0) kidInvalid[previousKey] = true;
+      ninKidUsed[hNin] = vKid;
+    }
+  }
+\end{lstlisting}
+\xdef\tpd{\the\prevdepth}
+\end{minipage}
+\item[] \underline{Features}
     \begin{itemize}
-      \item Sybil resistance. To prevent a Person from registering more than one $\khk$ using different identification documents, which are issued for the same $Nin$.
-      \item Loss of $\kid$. If a Person looses previously registered $\kid$ (e.g. by loosing the eID), they can register a new one.
-      \item Identity theft damage control. If a Person overwrites the previous $\kid$ with a new one, the identity thief will loose access to services that check the whole identity chain.
+      \item[] \textbf{Sybil resistance} \\ A Person is prevented from registering more than one $\khk$, e.g. by using different identification documents issued for the same $Nin$.
+          \vspace{5px}
+      \item[] \textbf{Fix for the loss of eID} \\ A Person who has lost a previously registered $\kid$, e.g. due to loss of eID, can overwrite it by registering a new $\kid$.
+          \vspace{5px}
+      \item[] \textbf{Identity theft damage control} \\ If a Person overwrites the previous $\kid$ with a new one, the identity Thief loses access to services that verify the entire identity chain.
     \end{itemize}
 
-    Entities who know $\kid$ (e.g. CA that issued it) can know that the Person is using \pbc{}, and what identification document the Person is using.
-
-  \item Register $\khk$ on \pbc, by calling 
-    $$register\khk(Nin\kid, Nin\kid\khk, proof)$$
-  where:
-    \begin{enumerate}
-      \item $Nin\kid=H(Nin,\kid^{-1}("register\khk"))$
-      \item $Nin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$
-    \end{enumerate}
+\item[] \underline{Remarks}
+\begin{itemize}
+\item[i)] An entity that knows $\kid$, e.g. the CA who certified the corresponding eID, can know that the Person has registered $\kid$ on \pbc{}.
+\item[ii)] Reasoning behind the choice of arguments: if $H(Nin, \kid^{-1}("register\kid"))$ was used as an argument, then TODO.
+On the other hand, the choice of arguments $Nin$ and $\kid^{-1}("register\kid")$ would TODO.
+\end{itemize}
 \end{enumerate}
@@
 \newpage
-\section{On chain code}
-\begin{lstlisting}[language=C, frame=single, style=b]
-//pseudo Solidity
-//Key is eID private key, or PrivateeIDKey("")
-//PersonKey is Blockchain key used by a Person
-contract IdentitiesManager {
-  //all the mappings are mappings where uint256 is a hash!
-  mapping(uint256 => uint256) public PinKUsed;
-  mapping(uint256 => uint256) public PinKPUsed;
-  mapping(uint256 => uint256) public PinKPLastConfirmed;
-  mapping(uint256 => bool) public PInvalid;
-  mapping(uint256 => bool) public KInvalid;
-  //TODO:CA fields!
+\section{Registering $\khk$}
+Register $\khk$ on \pbc{} by calling $$register\khk(Nin\kid, Nin\kid\khk, proof),$$
+  where:
+    \begin{enumerate}
+      \item[] $Nin\kid=H(Nin,\kid^{-1}("register\khk"))$
+      \item[] $Nin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$.
+    \end{enumerate}
+\begin{enumerate}[leftmargin=0cm]
+\item[] \underline{Pseudo-solidity code}
 
-  //K_1=K_1("registerK")
-  //Pin=H(Pin)
-  function registerK public(
-    uint256 Pin,
-    uint256 K_1,
-    bytes proofPinOwnsK
-  ){
-    uint256 previousKey = PinKUsed[Pin];
-    if(previouseKey == K_1)
-      return;
-    bool isOwner = zksnarkverify(VK, [
-        PIN, 
-        K_1
-      ],
-      proofPINOwnsK);
-    if(isOwner && ! KInvalid[K_1]){
-      if(previousKey!=0)
-        KInvalid[previousKey]=true;
-      PinKUsed[Pin]=K_1;
+\hfill\begin{minipage}{\dimexpr\textwidth-20px}
+\begin{lstlisting}[language=Solidity]
+  mapping(uint256 => uint256) public ninKidKpUsed;
+  mapping(uint256 => bool) public kpInvalid;
+  mapping(uint256 => uint256) public ninKidKpLastConfirmed;
+
+  function registerKp(
+    uint256 ninKid,
+    uint256 ninKidKp,
+    bytes proof
+  ) public {
+    uint256 previousKey = ninKidKpUsed[ninKid];
+    if (previousKey == ninKid) return; // already registered
+    bool ok = zksnarkverify(VK, [ninKid, ninKidKp], proof); // VK = verification key
+    if (ok && !kpInvalid[ninKidKp]) {
+      if (previousKey != 0) kpInvalid[previousKey] = true;
+      ninKidKpUsed[ninKid] = ninKidKp;
+      ninKidKpLastConfirmed[ninKid] = block.number;
     }
   }
+\end{lstlisting}
+\xdef\tpd{\the\prevdepth}
+\end{minipage}
+\item[] \underline{Features}
+\begin{itemize}
+      \item[] \textbf{Sybil resistance} \\ $\khk$ is a unique public key bound to the Person on the \pbc{}. By design, the Person cannot have two valid $\khk$ keys at the same time.
 
-  //PinK=H(Pin, K_1("registerP")) which is != H(Pin, K_1("registerK"))
-  //PinK can not be connected to Pin, unless one knows K_1
-  function registerP public(
-    uint256 PinK,
-    uint256 PinKP,
-    bytes proof
-  ){
-    uint256 previousKey = PinKPUsed[PinK]
-    if(previousKey == PinK)
-      return; //already registered
+      TODO: Explanation/proof.
+      \vspace{5px}
+    \item[] \textbf{Anonimity} \\ No one who has a database with all public keys $\kid$ or/and public keys $\khk$ can tell, from the function call, which $Nin$, $\kid$ or $\khk$ was used.
+This is true under the assumption that CA, which certified the eID, does not have access to $\kid^{-1}$, i.e.
+that $\kid$ was securely generated on the eID.
 
-    //zkp(
-      //K!invalid
-        //?Need KInvalid to be Zero Knowledge Set (ZKS), and to get roots
-      //CA!invalid
-      //CA -> K -> Pin
-      //PinK=H(Pin, K_1("registerP"))
-      //PinKP=H(Pin, K_1("registerP"), P_1("registerP"))
-    //)
-    bool ok = zksnarkverify(VK, [
-    ], proof);
+    TODO: Explanation/proof.
+\end{itemize}
 
-    if(ok && ! PInvalid[PinKP]){
-      if(previousKey != 0)
-        PInvalid[previousKey]=true;
-      PinKPUsed[PinK]=PinKP;
-      PinKPLastConfirmed[PinK]=block.number;
-    }
+\item[] \underline{Remarks}
+\begin{itemize}
+\item[i)] Reasoning behind the choice of arguments: TODO
+\end{itemize}
 
-  }
-
-}
-
-contract PersonAccount{
-}
-\end{lstlisting}
+\end{enumerate}
 
@@
 \section{zkp code}
-\begin{lstlisting}[language=C, frame=single, style=b]
+\begin{lstlisting}
 //pseudo zokrates zk-SNARK
@@
 \section{Problems}
-\begin{problem}
-  The rate of adding identities, the problem being frequent changes of Merkle Tree Roots, and how long it takes to generate zkp proof, and block generation time.
-\end{problem}
-\begin{problem}
-\label{prob:bigsteal}
-  Someone stole $K^{-1}$ before we registered on \pbc.
-  The Thief registered $K$ and $P$, and who knows what else.
-\end{problem}
-\begin{solution}
-\end{solution}
-\begin{problem}
-  Someone stole $K^{-1}$ after we registered on \pbc.
-\end{problem}
-\begin{problem}
-Trying to use unregistered Key.
-\end{problem}
-\begin{solution}
-\end{solution}
-\begin{problem}
-Trying to register the same PIN with multiple Keys (e.g. two physical ids).
-\end{problem}
-\begin{problem}
-\label{prob:chain}
-  Using $P$ without checking the whole $CA\rightarrow K\rightarrow P$ chain.
+\begin{enumerate}[label=\textbf{P\arabic*}]
+\item The rate of addition of identities, the problems of frequent changes of Merkle Tree Roots, and how long it takes to generate zkp proof, and block generation time.
+\item \label{bigsteal} The Thief stole $\kid^{-1}$ before we registered on \pbc{} and then registered $\kid$ and $\khk$.
+\item The Thief stole $\kid^{-1}$ after we registered on \pbc.
+\item Trying to use unregistered Key.
+\item Trying to register the same $Nin$ with multiple Keys (e.g. two physical ids).
+\item \label{chain} Using $\khk$ without checking the whole $CA\rightarrow \kid \rightarrow \khk$ chain.
   \begin{itemize}
-    \item Using $P$ to register as a mining key.
-    \item Invalidating $P$.
-    \item Using $P_{new}$ as a mining key.
+    \item[i)] Using $\khk$ to register as a mining key.
+    \item[ii)] Invalidating $\khk$.
+    \item[iii)] Using new $\khk$ as a mining key.
   \end{itemize}
-\end{problem}
-\begin{solution}
-  Look at the solution to Problem \ref{prob:miningKey}.
+  \underline{Solution}
 
-  The Mining Registry can accept new $P$s after an expiration period (which can also be e.g. 1 day).
-\end{solution}
-\begin{problem}
-\label{prob:miningKey}
-  A combination of Problem \ref{prob:bigsteal} and Problem \ref{prob:chain}.
-  Someone steals $K$, registeres $P$ and registeres $P$ for mining.
-  The problem is bigger, because we can't invalidate $P$ if we don't know which $P$ it is.
-\end{problem}
-\begin{solution}
-  We make $P$ renewable. We write the last block number it was renewed on to the blockchain.
-  Mining Registry can choose to accept P which is not older than some time period (for the Registry a good period would seem to be 1 day).
-  When paying the miners, the Registry also requires proof of $P$'s age.
+  Look at the solution to \ref{miningKey}.
 
-  $K$ is easely invalidated, because there is an explicit $PIN \rightarrow K^{-1}$ mapping on the blockchain, so it doesn't need to be renewable in the sence to proove it is still valid.
-\end{solution}
-\begin{problem}
-  Only $P$ compromised.
-\end{problem}
+  The Mining Registry can accept new $\khk$ after an expiration period (which can be e.g. one day).
+\item \label{miningKey} A combination of \ref{bigsteal} and \ref{chain}.
+The Thief steals $\kid$, registers $\khk$ and registers $\khk$ for mining.
+The problem is bigger, because we can't invalidate $\khk$ if we don't know which $\khk$ it is.
+
+  \underline{Solution}
+
+  We make $\khk$ renewable. We write the last block number it was renewed on to the \pbc.
+  Mining Registry can choose to accept $\khk$ that is not older than some time period (for the Registry a good period would seem to be one day).
+  When paying the miners, the Registry also requires proof of $\khk$.
+\item Only $\khk$ is compromised.
+\end{enumerate}
 \end{document}

### 2022-06-28 paper.tex
updated README

@@
  \arrayrulecolor{gray}
-\begin{tabular}{p{0.16\linewidth}| p{0.84\linewidth}}
+\begin{tabular}{p{0.16\linewidth}| p{0.81\linewidth}}
   $(K, K^{-1})$ & \ \ Pair of public key $K$ and the corresponding private key $K^{-1}$ \\[3px]
@@
 \item[i)] An entity that knows $\kid$, e.g. the CA who certified the corresponding eID, can know that the Person has registered $\kid$ on \pbc{}.
-\item[ii)] Reasoning behind the choice of arguments: if $H(Nin, \kid^{-1}("register\kid"))$ was used as an argument, then TODO.
+\item[ii)] Reasoning for the choice of arguments: if $H(Nin, \kid^{-1}("register\kid"))$ was used as an argument, then TODO.
 On the other hand, the choice of arguments $Nin$ and $\kid^{-1}("register\kid")$ would TODO.

### 2022-07-09 paper.tex
updated README
none

@@
 
+\lstdefinelanguage{circom}{
+	keywords=[1]{signal, input, output, public, template, component, var, function, return, if, else, for, while,
+		do, log, assert, include, pragma, circom}, % generic keywords including crypto operations
+	keywordstyle=[1]\color{blue}\bfseries,
+	keywords=[2]{},	% types; money and time units
+	keywordstyle=[2]\color{teal}\bfseries,
+	keywords=[3]{},	% environment variables
+	keywordstyle=[3]\color{violet}\bfseries,
+	identifierstyle=\color{black},
+	sensitive=false,
+	comment=[l]{//},
+	morecomment=[s]{/*}{*/},
+	commentstyle=\color{gray}\ttfamily,
+	stringstyle=\color{red}\ttfamily,
+	morestring=[b]',
+	morestring=[b]"
+}
+
+\lstset{
+	language=circom,
+	backgroundcolor=\color{verylightblue},
+	extendedchars=true,
+	basicstyle=\footnotesize\ttfamily,
+	showstringspaces=false,
+	showspaces=false,
+	numbers=left,
+	numberstyle=\footnotesize,
+	numbersep=9pt,
+	tabsize=2,
+	breaklines=true,
+	showtabs=false,
+	captionpos=b
+}
+
 \newcommand{\khk}{K_{P}}
@@
 Albert Vučinović, University North\\
-Miroslav Jerković, University of Zagreb
-}
+Miroslav Jerković, University of Zagreb}
 \begin{document}
@@
 \end{minipage}
+
+\item[] \underline{Pseudo-circom code}
+
+\hfill\begin{minipage}{\dimexpr\textwidth-20px}
+\begin{lstlisting}[language=circom]
+pragma circom 2.0.0;
+
+template NinOwnsKid(){
+	//TODO: What happens to uint256 when converted to signal
+
+	//public:
+	signal input hNin;
+	signal input vKid;
+
+	//private:
+
+	//Take Kid
+	//Take CA
+
+}
+component main { public [hNin,vKid]} = NinOwnsKid();
+\end{lstlisting}
+\xdef\tpd{\the\prevdepth}
+\end{minipage}
+
 \item[] \underline{Features}

### 2022-07-09 paper.tex
circom Nin owns Kid

@@
 	language=circom,
-	backgroundcolor=\color{verylightblue},
+	backgroundcolor=\color{lightgray},
 	extendedchars=true,
@@
 \hfill\begin{minipage}{\dimexpr\textwidth-20px}
+Using https://github.com/zkp-application/circom-rsa-verify for now, MIT license.
+Which probably doesn't work, we should check (sha256?).
+The next line is used on a file of shape:
+-----BEGIN PUBLIC KEY-----
+...
+-----END PUBLIC KEY-----
+-----BEGIN CERTIFICATE-----
+...
+-----END CERTIFICATE-----
+We assume: 
+	modulus = Subject Modulus
+	exp = Subject Exponent
+
+openssl x509 -in Identification.pem -text -noout
+
 \begin{lstlisting}[language=circom]
@@
 
-template NinOwnsKid(){
+include "./utils/rsa_verify.circom"
+include "./circomlib/circuits/sha256/sha256.circom"
+include "./circomlib/bitify.circom"
+
+//hashNumberOfWords = 4 for sha256
+//rsaNumberOfWords = 32 for 2048 rsa
+//we use words of 64 bits
+template NinOwnsKid(
+		rsaNumberOfWords, 
+		hashNumberOfWords, 
+		lengthInBitsOfSignedMessage,
+		lengthOfNinInBits
+){
 	//TODO: What happens to uint256 when converted to signal
@@
 	//private:
+	signal input Nin;
+	//Kid, CA signature
+	singal input exp[rsaNumberOfWords];
+	signal input sign[rsaNumberOfWords];
+	signal input modulus[rsaNumberOfWords];
+
+	//we need some inputs to verify what is signed
+	//and that Nin in the right place in the signed message
+  signal input messageToBeSigned[lengthInBitsOfSignedMessage];
+	signal input Nin[lengthOfNinInBits];
+
+	//TODO: Insert Nin into messageToBeSigned in the right place
+	//or create constraint on the corresponding bits
+
+	component sha = Sha256(lengthInBitsOfSignedMessage);
+	for (int i = 0; i<lengthInBitsOfSignedMessage; i++) {
+		sha.in[i] <== messageToBeSigned[i]
+	}
+
+	var hashed[hashNumberOfWords];//4x64 bit
+	var hashedBits[hashNumberOfWords*64];
+	for (int i=0; i<hashNumberOfWords*64;i++){
+		hashedBits[i] <== sha.out[i];
+	}
+	component b2n = Bits2Num(64);
+	//TODO:Can we use a component multiple times?
+	//Will all the constraints be generated
+	for (int i=0;i<hashNumberOfWords;i++){
+		for (int j=0;j<64;j++){
+			b2n.in[j] <== hashedBits[i*64+j];
+		}
+	  hashed[i] <== b2n.out;
+	}
+
+	//lets assume sha256WithRSAEncryption
+
+	component rsa = RsaVerifyPkcs1v15(64, rsaNumberOfWords, 17, 4);
+	for (var i = 0; i < rsaNumberOfWords; i++){
+		rsa.exp[i] <== exp[i];
+		rsa.sign[i] <== sign[i];
+		rsa.modulus[i] <== modulus[i];
+	}
+	for (var i = 0; i<hashNumberOfWords; i++){
+		rsa.hashed[i] <== hashed[i];
+	}
+
+	//Check CA on CA approved list
+	//On blockchain mapping (uint256 => bool) public CAValid
 

### 2022-07-23 paper.tex
Human readable points we need to prove in the first proof (NinOwnsKid)

@@
 
-\hfill\begin{minipage}{\dimexpr\textwidth-20px}
 Using https://github.com/zkp-application/circom-rsa-verify for now, MIT license.
-Which probably doesn't work, we should check (sha256?).
-The next line is used on a file of shape:
------BEGIN PUBLIC KEY-----
-...
------END PUBLIC KEY-----
------BEGIN CERTIFICATE-----
-...
------END CERTIFICATE-----
-We assume: 
-	modulus = Subject Modulus
-	exp = Subject Exponent
+Which probably doesn't work, we should check (sha256?). \\
+The next line is used on a file of shape:\\
+-----BEGIN PUBLIC KEY-----\\
+...\\
+-----END PUBLIC KEY-----\\
+-----BEGIN CERTIFICATE-----\\
+...\\
+-----END CERTIFICATE-----\\
+We assume: \\
+	modulus = Subject Modulus\\
+	exp = Subject Exponent\\
+openssl x509 -in Identification.pem -text -noout\\
 
-openssl x509 -in Identification.pem -text -noout
+Statements we need to check:
+\begin{itemize}
+	\item CA is an accepted CA by \pbc{}
+		\begin{itemize}
+			\item A set representation  exists on blockchain which contains CA public keys (CA-public-keys).
+			\item Verify inclusion of the CA in cert in CA-public-keys.
+			\item A set representation exists on blockchain which has all the revoked CA public keys (Revoked-CA-public-keys).
+			\item Verify exclusion of the CA in cert from Revoked-CA-public-keys.
+			\item Verify CA validity with respect to time (maybe blockchain)
+		\end{itemize}
+	\item Cert CA signed 
+		\begin{itemize}
+			\item the Kid
+			\item x509 Subject that contains Nin in the right place in the subject
+			\item verify Validity of x509 cert with respect to time
+		\end{itemize}
+	\item Kid is not on revoked certs list by CA (blockchain hosted list)
+	\item Kid decrypts vKid into clear text "registerKid".
+\end{itemize}
 
@@
 		lengthInBitsOfSignedMessage,
-		lengthOfNinInBits
+		lengthOfNinInBits,
+		bitsInAWord
 ){
@@
 	var hashed[hashNumberOfWords];//4x64 bit
-	var hashedBits[hashNumberOfWords*64];
-	for (int i=0; i<hashNumberOfWords*64;i++){
+	var hashedBits[hashNumberOfWords*bitsInAWord];
+	for (int i=0; i<hashNumberOfWords*bitsInAWord;i++){
 		hashedBits[i] <== sha.out[i];
@@
 	for (int i=0;i<hashNumberOfWords;i++){
-		for (int j=0;j<64;j++){
+		for (int j=0;j<bitsInAWord;j++){
 			b2n.in[j] <== hashedBits[i*64+j];
@@
 	//lets assume sha256WithRSAEncryption
-
-	component rsa = RsaVerifyPkcs1v15(64, rsaNumberOfWords, 17, 4);
+	//verify CA signature of Kid
+	component rsa = RsaVerifyPkcs1v15(bitsInAWord, rsaNumberOfWords, 17, 4);
 	for (var i = 0; i < rsaNumberOfWords; i++){
@@
 	}
+
+	//TODO: verify Kid(vKid)=="registerKid"
 
@@
 \xdef\tpd{\the\prevdepth}
-\end{minipage}
 

### 2022-07-23 paper.tex
register solidity

@@
 \newpage
-\section{Registering $\kid$}
+\section{Registering identity key ($\khk$)}
 Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsKid).$$
@@
 \begin{lstlisting}[language=Solidity]
-  mapping(uint256 => uint256) public ninKidUsed;
-  mapping(uint256 => bool) public kidInvalid;
+  mapping(uint => uint) public ninKidUsed;
+	mapping(uint => uint) public ninKidKpUsed;
+  mapping(uint => bool) public kidInvalid;
 
-  function registerKid(
-    uint256 hNin, // hNin = H(Nin)
-    uint256 vKid, // vKid = KidPrivate("registerKid")
-    bytes proofNinOwnsKid
+  function register(
+    uint hNin, // hNin = H(Nin)
+		uint hNinKid,
+		uint hNinKidKp,
+		bool invalidate, //true if someone stole your previous id
+		uint[2] memory proofPointA,
+		uint[2][2] memory proofPointsB,
+		uint[2] memory proofPointC,
   ) public {
-    uint256 previousKey = ninKidUsed[hNin];
-    if (previousKey == vKid) return; // already registered
-    bool isOwner = zksnarkverify(VK, [hNin, vKid], proofNinOwnsKid); // VK = verification key
-    if (isOwner && !kidInvalid[vKid]) {
-      if (previousKey != 0) kidInvalid[previousKey] = true;
-      ninKidUsed[hNin] = vKid;
+		//Setting public arguments
+		uint[] memory inputValues = new uint[](3);
+		inputValues[0]=hNin;
+		inputValues[1]=hNinKid;
+		inputValues[2]=hNinKidKp;
+
+    require(verifyProof(
+			proofPointA,
+			proofPointsB,
+			proofPointC,
+			inputValues
+		));
+
+    uint previousHNinKid = ninKidUsed[hNin];
+    if (previousHNinKid != hNinKid and invalidate == true) {
+			//If they are different, we need to invalidate old Kid
+			kidInvalid[previousHNinKid] = true;
 		}
+		require(!kidInvalid[hNinKid]);
+
+		ninKidUsed[hNin] = hNinKid;
+
+		ninKidKpUsed[hNinKid] = hNinKidKp;
+
   }
+
 \end{lstlisting}
@@
 \item[i)] An entity that knows $\kid$, e.g. the CA who certified the corresponding eID, can know that the Person has registered $\kid$ on \pbc{}.
-\item[ii)] Reasoning for the choice of arguments: if $H(Nin, \kid^{-1}("register\kid"))$ was used as an argument, then TODO.
-On the other hand, the choice of arguments $Nin$ and $\kid^{-1}("register\kid")$ would TODO.
+\item[ii)] Reasoning for the choice of arguments: if $H(Nin, \kid^{-1}("register\kid"))$ was used as an argument, then if someone tried to register with two different ids, we couldn't tell if $Nin$ was already used.
+On the other hand, the choice of arguments $Nin$ and $\kid^{-1}("register\kid")$ would be almost the same as $hNin$ and $\kid^{-1}("register\kid")$, because you can brute force all the possible $Nin$s and find the corresponding $hNins$.
 \end{itemize}
@@
 \begin{itemize}
-\item[i)] Reasoning behind the choice of arguments: TODO
+\item[i)] Reasoning behind the choice of arguments:
+We want to connect $Nin$ with $\khk$ in a unique, but untraceable way.
+If we only used $Nin\kid\khk$ then if someone used multiple $\khk$s we wouldn't be able to prove the connection to $Nin$ (i.e. they could register a lot of $\khk$s).
+Hashing connects arguments, and makes them opaque without the knowledge of arguments (which in this case include private keys), so the arguments are opaque without the knowledge of private keys.
 \end{itemize}
@@
 \newpage
-\section{zkp code}
+\underline{Pseudo-circom code}
+Statements we need to check:
+\begin{itemize}
+	\item Check first step (Register $\kid$) still valid
+
+\end{itemize}
+
 \begin{lstlisting}

### 2022-07-23 paper.tex
registerKid using verifyProof

@@
 \newpage
-\section{Registering identity key ($\khk$)}
+\section{Registering $\kid$}
 Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsKid).$$
@@
   mapping(uint => uint) public ninKidUsed;
-	mapping(uint => uint) public ninKidKpUsed;
   mapping(uint => bool) public kidInvalid;
 
-  function register(
+  function registerKid(
     uint hNin, // hNin = H(Nin)
-		uint hNinKid,
-		uint hNinKidKp,
-		bool invalidate, //true if someone stole your previous id
+    uint vKid, // vKid = KidPrivate("registerKid")
 		uint[2] memory proofPointA,
-		uint[2][2] memory proofPointsB,
+		uint[2][2] memory proofPointB,
 		uint[2] memory proofPointC,
+		bool invalidate
   ) public {
 		//Setting public arguments
-		uint[] memory inputValues = new uint[](3);
-		inputValues[0]=hNin;
-		inputValues[1]=hNinKid;
-		inputValues[2]=hNinKidKp;
+		uint[] memory inputValues = new uint[](2)
+		inputValues[0] = hNin;
+		inputValues[1] = vKid;
 
-    require(verifyProof(
+		require(
+			verifyProof(
 				proofPointA,
-			proofPointsB,
+				proofPointB,
 				proofPointC,
 				inputValues
-		));
+			)
+		);
 
-    uint previousHNinKid = ninKidUsed[hNin];
-    if (previousHNinKid != hNinKid and invalidate == true) {
+    uint previousKey = ninKidUsed[hNin];
+    if (previousKey == vKid) return; // already registered
+
+ 		uint previousVKid = ninKidUsed[hNin];
+    if (previousVKid != vKid and invalidate == true) {
 			//If they are different, we need to invalidate old Kid
-			kidInvalid[previousHNinKid] = true;
+			kidInvalid[previousVKid] = true;
 		}
-		require(!kidInvalid[hNinKid]);
+		require(!kidInvalid[vKid]);
 
-		ninKidUsed[hNin] = hNinKid;
-
-		ninKidKpUsed[hNinKid] = hNinKidKp;
-
+    ninKidUsed[hNin] = vKid;
   }
-
 \end{lstlisting}
@@
 \begin{itemize}
-	\item Check first step (Register $\kid$) still valid
-
+	\item CA
 \end{itemize}

### 2022-07-23 paper.tex
registerKp using verifyProof

@@
 \begin{lstlisting}[language=Solidity]
-  mapping(uint256 => uint256) public ninKidKpUsed;
-  mapping(uint256 => bool) public kpInvalid;
-  mapping(uint256 => uint256) public ninKidKpLastConfirmed;
+  mapping(uint => uint) public ninKidKpUsed;
 
   function registerKp(
-    uint256 ninKid,
-    uint256 ninKidKp,
-    bytes proof
+    uint hNinKid,
+    uint hNinKidKp,
+		uint[2] memory proofPointA,
+		uint[2][2] memory proofPointsB,
+		uint[2] memory proofPointC
   ) public {
-    uint256 previousKey = ninKidKpUsed[ninKid];
-    if (previousKey == ninKid) return; // already registered
-    bool ok = zksnarkverify(VK, [ninKid, ninKidKp], proof); // VK = verification key
-    if (ok && !kpInvalid[ninKidKp]) {
-      if (previousKey != 0) kpInvalid[previousKey] = true;
-      ninKidKpUsed[ninKid] = ninKidKp;
-      ninKidKpLastConfirmed[ninKid] = block.number;
-    }
+
+		//Setting public arguments
+		uint[] memory inputValues = new uint[](2)
+		inputValues[0] = hNinKid;
+		inputValues[1] = hNinKidKp;
+
+		require(
+			verifyProof(
+				proofPointA,
+				proofPointsB,
+				proofPointC,
+				inputValues
+			)
+		);
+
+    ninKidKpUsed[hNinKid] = hNinKidKp;
   }

### 2022-07-23 paper.tex
cleanup

@@
 
-\begin{lstlisting}
-//pseudo zokrates zk-SNARK
-import "hashes/sha256/512bitPacked" as sha256packed
-import "ecc/babyjubjubParams.code" as context
-import "ecc/proofOfOwnership.code" as proofOfOwnership
-
-def proofPINOwnsK(
-  field[2] PINHash,
-  field[2] K_1Hash,
-  field[2]
-
-  private field[?] CACert){
-}
-
-def proof_of_being_a_person(
-  //publically known arguments
-  field[2] PINKeyUsedHash,
-  field[2] PINKeyPersonKeyIssuedHash,
-  field[2] PersonKeyInvalidHash,
-  field[2] KeyInvalidHash,
-
-  //BC state
-  field BC_PINUsed,//BC State
-  field BC_PINKeyUsed,//BC State
-  field BC_PINKeyPersonKeyIssued,//BC State
-  field BC_PersonKeyInvalid,//BC State
-  field BC_KeyInvalid,//BC State
-  ?field BC_private_key_challenge?
-
-  //CA keys!
-  field[?][?] CAKeys,//? BC State
-  ...
-
-  //private data
-  //15360 bit RSA key is equivalent to 256-bit symmetric keys
-  //2048 bit RSA key is equivalent to 112 bit symmetric keys
-  //eID has 2048 bit RSA
-  private field PIN,//max 254 bits, using only 128 = 16 bytes
-  private field K_private_bc_new,//ECC private key
-  private field[?] K_new,//public RSA key from eID
-  private field[?] K_1_new,//private RSA key from eID, actually signed message
-  //K_1_new("PeopleBC person proof")
-  private field K_private_bc_old,//ECC private key, old
-  private field[?] K_1_old)//K_1_old("PeopleBC person proof")?
-  //?private field[2] K_bc_new,//ECC public key ?no need for key pair verification?
-  //?private field[2] K_bc_old,//ECC public key ?no need for key pair verification
-  private field[?] CAcert,
-  private field CAindex
-{
-  //actual checking code here
-  field[2] hash_PIN = sha256packed([0,0,0,PIN])
-  assert(hash_PIN == PINHash);//proving that we know the real PIN, unimportant
-
-  //proving ownership of newly registered key,
-  //no real need to prove ownership of bc key
-  //we actually need to prove ownereship of K_1_new,
-  //and its connection to PIN via CA
-  context=context()//babyjubjubParams context
-  proofOfOwnership(K_bc_new, K_private_bc_new, context)==1
-
-  //prove that you own the K_new
-  //pseudo
-  RSADecrypt(K_new, K_1_new) == "PeopleBC Person Proof";//?+BC_private_key_challenge;
-
-  //proove that Key is connected to CA
-  //pseudo
-  checkCASignature(CAKey[CAindex], CACert, K_new) == 1;
-
-  //proove that K_new is PIN certificate
-  //pseudo
-  extractPIN(CACert)==PIN;
-
-  //end
-
-  //end..
-}
-\end{lstlisting}
 \newpage

### 2022-07-23 paper.tex
Statements to check registerP

@@
   mapping(uint => uint) public ninKidKpUsed;
+	mapping(uint => bool) public isPerson;
 
@@
     uint hNinKidKp,
+		uint Kp,
 		uint[2] memory proofPointA,
@@
 		//Setting public arguments
-		uint[] memory inputValues = new uint[](2)
+		uint[] memory inputValues = new uint[](3)
 		inputValues[0] = hNinKid;
 		inputValues[1] = hNinKidKp;
+		inputValues[2] = Kp;
 
@@
     ninKidKpUsed[hNinKid] = hNinKidKp;
+		isPerson[Kp]=true;
   }
@@
 \begin{itemize}
-	\item CA
+	\item Check first step (Register $\kid$) still valid
+	\item Check hNinKid valid
+	\item Check hNinKidKp valid
+	\item Check Kp valid
+	\item TODO: Kp invalidation!?
 \end{itemize}

### 2022-07-24 paper.tex
PoI paper general editing

--- 2022-07-23 paper.tex
@@
 	language=circom,
-	backgroundcolor=\color{lightgray},
+	backgroundcolor=\color{verylightgray},
 	extendedchars=true,
@@
 
-\newcommand{\khk}{K_{P}}
+\newcommand{\khk}{K_{H}}
 \newcommand{\khkp}{$K^{-1}[\text{HK}]$}
@@
 	$\kid$ & \ \ CA-certified public key of eID\\[3px]
-  $\khk$ & \ \ Person key, unique public key used to access \pbc{}
+  $\khk$ & \ \ Human key, unique public key to access \pbc{}
 
@@
 \section{Registering $\kid$}
-Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsKid).$$
+Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), invalidate\kid, verifyProofArguments).$$
 \begin{enumerate}[leftmargin=0cm]
+
 	\item[] \underline{Pseudo-solidity code}
@@
 	\begin{lstlisting}[language=Solidity]
+	pragma solidity ^0.8.0;
+
 	mapping(uint => uint) public ninKidUsed;
@@
 		uint vKid, // vKid = KidPrivate("registerKid")
+		bool invalidateKid,
 		uint[2] memory proofPointA,
 		uint[2][2] memory proofPointB,
-		uint[2] memory proofPointC,
-		bool invalidate
+		uint[2] memory proofPointC
 	) public {
-		//Setting public arguments
-		uint[] memory inputValues = new uint[](2)
+		// Setting public arguments
+		uint[] memory inputValues = new uint[](2);
 		inputValues[0] = hNin;
@@
 		require(
-			verifyProof(
-				proofPointA,
-				proofPointB,
-				proofPointC,
-				inputValues
-			)
+			verifyProof(proofPointA, proofPointB, proofPointC, inputValues)
 		);
@@
 		uint previousVKid = ninKidUsed[hNin];
-    if (previousVKid != vKid and invalidate == true) {
-			//If they are different, we need to invalidate old Kid
+		if (previousVKid != vKid && invalidateKid == true) {
+			// If they are different, invalidate old Kid
 			kidInvalid[previousVKid] = true;
@@
 
+	\item[] Features
+    \begin{itemize}
+      \item[] \textbf{Sybil resistance} \\ A Person is prevented from registering more than one $\khk$, e.g. by using different eIDs issued for the same $Nin$.
+          \vspace{5px}
+      \item[] \textbf{Fix for the loss of eID} \\ A Person who has lost a previously registered $\kid$, e.g. due to loss of eID, can overwrite it by registering a new $\kid$.
+          \vspace{5px}
+      \item[] \textbf{Identity theft damage control} \\ If a Person overwrites the previous $\kid$ with a new one, the identity Thief loses access to services that verify the entire identity chain.
+    \end{itemize}
+
+\item[] Remarks
+\begin{itemize}
+\item[i)] An entity that knows $\kid$, e.g. the CA who certified the corresponding eID, can know that the Person has registered $\kid$ on \pbc{}.
+\item[ii)] Reasoning for the choice of arguments $H(Nin)$ and $\kid^{-1}("register\kid")$: 
+\begin{itemize}
+	\item[-] if $H(Nin, \kid^{-1}("register\kid"))$ was instead used, then if someone tried to register with two different eIDs, we couldn't tell if $Nin$ was already used. 
+	\item[-] the choice of arguments $Nin$ and $\kid^{-1}("register\kid")$ would be almost the same as $H(Nin)$ and $\kid^{-1}("register\kid")$, because you can brute force all the possible $Nin$s and find the corresponding $H(Nin)$s.
+\end{itemize}
+\end{itemize}
+
 \item[] \underline{Pseudo-circom code}
 
-Using https://github.com/zkp-application/circom-rsa-verify for now, MIT license.
-Which probably doesn't work, we should check (sha256?). \\
+Statements we need to check:
+\begin{itemize}
+	\item[1)] CA is accepted by \pbc{} (assumption: the set representations of \textit{CA-public-keys} and \textit{revoked-CA-public-keys} lists exist on \pbc{}):
+		\begin{itemize}
+			\item[i)] inclusion of the CA in cert in \textit{CA-public-keys}.
+			\item[ii)] exclusion of the CA in cert from \textit{revoked-CA-public-keys}.
+		\end{itemize}
+		Verify CA validity with respect to time (maybe on \pbc{})!
+	\item[2)] Cert CA signed: 
+		\begin{itemize}
+			\item[i)] $\kid$
+			\item[ii)] x509 Subject that contains $Nin$ in the right place in the subject
+		\end{itemize}
+		Verify validity of x509 certificate with respect to time!
+		\item[3)] $\kid$ is not revoked by CA (\pbc{} hosted list)
+	\item[4)] $\kid$ decrypts $\kid^{-1}("register\kid")$ into clear text "registerKid".
+\end{itemize}
+
+For now, we're using the MIT-licensed \href{https://github.com/zkp-application/circom-rsa-verify}{Circom RSA signature verify}, which probably doesn't work - we should check (sha256?). \\
+
 The next line is used on a file of shape:\\
@@
 -----END CERTIFICATE-----\\
+
 We assume: \\
@@
 openssl x509 -in Identification.pem -text -noout\\
-
-Statements we need to check:
-\begin{itemize}
-	\item CA is an accepted CA by \pbc{}
-		\begin{itemize}
-			\item A set representation  exists on blockchain which contains CA public keys (CA-public-keys).
-			\item Verify inclusion of the CA in cert in CA-public-keys.
-			\item A set representation exists on blockchain which has all the revoked CA public keys (Revoked-CA-public-keys).
-			\item Verify exclusion of the CA in cert from Revoked-CA-public-keys.
-			\item Verify CA validity with respect to time (maybe blockchain)
-		\end{itemize}
-	\item Cert CA signed 
-		\begin{itemize}
-			\item the Kid
-			\item x509 Subject that contains Nin in the right place in the subject
-			\item verify Validity of x509 cert with respect to time
-		\end{itemize}
-	\item Kid is not on revoked certs list by CA (blockchain hosted list)
-	\item Kid decrypts vKid into clear text "registerKid".
-\end{itemize}
 
@@
 	//Kid, CA signature
-	singal input exp[rsaNumberOfWords];
+	signal input exp[rsaNumberOfWords];
 	signal input sign[rsaNumberOfWords];
@@
 
-\item[] \underline{Features}
-    \begin{itemize}
-      \item[] \textbf{Sybil resistance} \\ A Person is prevented from registering more than one $\khk$, e.g. by using different identification documents issued for the same $Nin$.
-          \vspace{5px}
-      \item[] \textbf{Fix for the loss of eID} \\ A Person who has lost a previously registered $\kid$, e.g. due to loss of eID, can overwrite it by registering a new $\kid$.
-          \vspace{5px}
-      \item[] \textbf{Identity theft damage control} \\ If a Person overwrites the previous $\kid$ with a new one, the identity Thief loses access to services that verify the entire identity chain.
-    \end{itemize}
-
-\item[] \underline{Remarks}
-\begin{itemize}
-\item[i)] An entity that knows $\kid$, e.g. the CA who certified the corresponding eID, can know that the Person has registered $\kid$ on \pbc{}.
-\item[ii)] Reasoning for the choice of arguments: if $H(Nin, \kid^{-1}("register\kid"))$ was used as an argument, then if someone tried to register with two different ids, we couldn't tell if $Nin$ was already used.
-On the other hand, the choice of arguments $Nin$ and $\kid^{-1}("register\kid")$ would be almost the same as $hNin$ and $\kid^{-1}("register\kid")$, because you can brute force all the possible $Nin$s and find the corresponding $hNins$.
-\end{itemize}
 \end{enumerate}
@@
 \section{Registering $\khk$}
-Register $\khk$ on \pbc{} by calling $$register\khk(Nin\kid, Nin\kid\khk, proof),$$
+Register $\khk$ on \pbc{} by calling $$register\khk(HNin\kid, HNin\kid\khk, \khk, verifyProofArguments),$$
   where:
     \begin{enumerate}
-      \item[] $Nin\kid=H(Nin,\kid^{-1}("register\khk"))$
-      \item[] $Nin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$.
+      \item[] $HNin\kid=H(Nin,\kid^{-1}("register\khk"))$
+      \item[] $HNin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$.
     \end{enumerate}
@@
 	\begin{lstlisting}[language=Solidity]
-  mapping(uint => uint) public ninKidKpUsed;
+	mapping(uint => uint) public ninKidKhUsed;
+	mapping(uint => bool) public isPerson;
 
-  function registerKp(
+	function registerKh(
 		uint hNinKid,
-    uint hNinKidKp,
+		uint hNinKidKh,
+		uint Kh,
 		uint[2] memory proofPointA,
@@
 	) public {
-
 		//Setting public arguments
-		uint[] memory inputValues = new uint[](2)
+		uint[] memory inputValues = new uint[](3);
 		inputValues[0] = hNinKid;
-		inputValues[1] = hNinKidKp;
+		inputValues[1] = hNinKidKh;
+		inputValues[2] = Kh;
 
 		require(
-			verifyProof(
-				proofPointA,
-				proofPointsB,
-				proofPointC,
-				inputValues
-			)
+			verifyProof(proofPointA, proofPointsB, proofPointC, inputValues)
 		);
 
-    ninKidKpUsed[hNinKid] = hNinKidKp;
+		ninKidKhUsed[hNinKid] = hNinKidKh;
+		isPerson[Kh] = true;
 	}
@@
 	\end{minipage}
-\item[] \underline{Features}
+
+	\item[] Features
 	\begin{itemize}
@@
 
-\item[] \underline{Remarks}
+	\item[] Remarks
 	\begin{itemize}
@@
 	We want to connect $Nin$ with $\khk$ in a unique, but untraceable way.
-If we only used $Nin\kid\khk$ then if someone used multiple $\khk$s we wouldn't be able to prove the connection to $Nin$ (i.e. they could register a lot of $\khk$s).
+	If we only used $HNin\kid\khk$ then if someone used multiple $\khk$s we wouldn't be able to prove the connection to $Nin$ (i.e. they could register a lot of $\khk$s).
 	Hashing connects arguments, and makes them opaque without the knowledge of arguments (which in this case include private keys), so the arguments are opaque without the knowledge of private keys.
@@
 
-\end{enumerate}
+\item[] \underline{Pseudo-circom code}
 
-\newpage
-\underline{Pseudo-circom code}
 Statements we need to check:
 \begin{itemize}
-	\item CA
+	\item[1)] $register\kid$ is still valid
+	\item[2)] $HNin\kid$ is valid
+	\item[3)] $HNin\kid\khk$ is valid
+	\item[4)] $\khk$ is valid
+	\item[5)] TODO: $\khk$ invalidation!?
 \end{itemize}
+
+\begin{lstlisting}[language=circom]
+	pragma circom 2.0.0;
+\end{lstlisting}
+
+\end{enumerate}
 

### 2022-07-26 paper.tex
Revert "register solidity"
This reverts commit 29148cfb8f94918c2a38bb46a824bf26e8b24ba5.

--- 2022-07-23 paper.tex
@@
 \begin{lstlisting}[language=Solidity]
-  mapping(uint => uint) public ninKidUsed;
-  mapping(uint => bool) public kidInvalid;
+  mapping(uint256 => uint256) public ninKidUsed;
+  mapping(uint256 => bool) public kidInvalid;
 
   function registerKid(
-    uint hNin, // hNin = H(Nin)
-    uint vKid, // vKid = KidPrivate("registerKid")
-		uint[2] memory proofPointA,
-		uint[2][2] memory proofPointB,
-		uint[2] memory proofPointC,
-		bool invalidate
+    uint256 hNin, // hNin = H(Nin)
+    uint256 vKid, // vKid = KidPrivate("registerKid")
+    bytes proofNinOwnsKid
   ) public {
-		//Setting public arguments
-		uint[] memory inputValues = new uint[](2)
-		inputValues[0] = hNin;
-		inputValues[1] = vKid;
-
-		require(
-			verifyProof(
-				proofPointA,
-				proofPointB,
-				proofPointC,
-				inputValues
-			)
-		);
-
-    uint previousKey = ninKidUsed[hNin];
+    uint256 previousKey = ninKidUsed[hNin];
     if (previousKey == vKid) return; // already registered
-
- 		uint previousVKid = ninKidUsed[hNin];
-    if (previousVKid != vKid and invalidate == true) {
-			//If they are different, we need to invalidate old Kid
-			kidInvalid[previousVKid] = true;
+    bool isOwner = zksnarkverify(VK, [hNin, vKid], proofNinOwnsKid); // VK = verification key
+    if (isOwner && !kidInvalid[vKid]) {
+      if (previousKey != 0) kidInvalid[previousKey] = true;
+      ninKidUsed[hNin] = vKid;
     }
-		require(!kidInvalid[vKid]);
-
-    ninKidUsed[hNin] = vKid;
   }
@@
 \begin{lstlisting}[language=Solidity]
-  mapping(uint => uint) public ninKidKpUsed;
+  mapping(uint256 => uint256) public ninKidKpUsed;
+  mapping(uint256 => bool) public kpInvalid;
+  mapping(uint256 => uint256) public ninKidKpLastConfirmed;
 
   function registerKp(
-    uint hNinKid,
-    uint hNinKidKp,
-		uint[2] memory proofPointA,
-		uint[2][2] memory proofPointsB,
-		uint[2] memory proofPointC
+    uint256 ninKid,
+    uint256 ninKidKp,
+    bytes proof
   ) public {
-
-		//Setting public arguments
-		uint[] memory inputValues = new uint[](2)
-		inputValues[0] = hNinKid;
-		inputValues[1] = hNinKidKp;
-
-		require(
-			verifyProof(
-				proofPointA,
-				proofPointsB,
-				proofPointC,
-				inputValues
-			)
-		);
-
-    ninKidKpUsed[hNinKid] = hNinKidKp;
+    uint256 previousKey = ninKidKpUsed[ninKid];
+    if (previousKey == ninKid) return; // already registered
+    bool ok = zksnarkverify(VK, [ninKid, ninKidKp], proof); // VK = verification key
+    if (ok && !kpInvalid[ninKidKp]) {
+      if (previousKey != 0) kpInvalid[previousKey] = true;
+      ninKidKpUsed[ninKid] = ninKidKp;
+      ninKidKpLastConfirmed[ninKid] = block.number;
+    }
   }
@@
 
+\begin{lstlisting}
+//pseudo zokrates zk-SNARK
+import "hashes/sha256/512bitPacked" as sha256packed
+import "ecc/babyjubjubParams.code" as context
+import "ecc/proofOfOwnership.code" as proofOfOwnership
+
+def proofPINOwnsK(
+  field[2] PINHash,
+  field[2] K_1Hash,
+  field[2]
+
+  private field[?] CACert){
+}
+
+def proof_of_being_a_person(
+  //publically known arguments
+  field[2] PINKeyUsedHash,
+  field[2] PINKeyPersonKeyIssuedHash,
+  field[2] PersonKeyInvalidHash,
+  field[2] KeyInvalidHash,
+
+  //BC state
+  field BC_PINUsed,//BC State
+  field BC_PINKeyUsed,//BC State
+  field BC_PINKeyPersonKeyIssued,//BC State
+  field BC_PersonKeyInvalid,//BC State
+  field BC_KeyInvalid,//BC State
+  ?field BC_private_key_challenge?
+
+  //CA keys!
+  field[?][?] CAKeys,//? BC State
+  ...
+
+  //private data
+  //15360 bit RSA key is equivalent to 256-bit symmetric keys
+  //2048 bit RSA key is equivalent to 112 bit symmetric keys
+  //eID has 2048 bit RSA
+  private field PIN,//max 254 bits, using only 128 = 16 bytes
+  private field K_private_bc_new,//ECC private key
+  private field[?] K_new,//public RSA key from eID
+  private field[?] K_1_new,//private RSA key from eID, actually signed message
+  //K_1_new("PeopleBC person proof")
+  private field K_private_bc_old,//ECC private key, old
+  private field[?] K_1_old)//K_1_old("PeopleBC person proof")?
+  //?private field[2] K_bc_new,//ECC public key ?no need for key pair verification?
+  //?private field[2] K_bc_old,//ECC public key ?no need for key pair verification
+  private field[?] CAcert,
+  private field CAindex
+{
+  //actual checking code here
+  field[2] hash_PIN = sha256packed([0,0,0,PIN])
+  assert(hash_PIN == PINHash);//proving that we know the real PIN, unimportant
+
+  //proving ownership of newly registered key,
+  //no real need to prove ownership of bc key
+  //we actually need to prove ownereship of K_1_new,
+  //and its connection to PIN via CA
+  context=context()//babyjubjubParams context
+  proofOfOwnership(K_bc_new, K_private_bc_new, context)==1
+
+  //prove that you own the K_new
+  //pseudo
+  RSADecrypt(K_new, K_1_new) == "PeopleBC Person Proof";//?+BC_private_key_challenge;
+
+  //proove that Key is connected to CA
+  //pseudo
+  checkCASignature(CAKey[CAindex], CACert, K_new) == 1;
+
+  //proove that K_new is PIN certificate
+  //pseudo
+  extractPIN(CACert)==PIN;
+
+  //end
+
+  //end..
+}
+\end{lstlisting}
 \newpage

### 2022-07-26 paper.tex

--- 2022-07-24 paper.tex
@@
 
-		uint previousKey = ninKidUsed[hNin];
-		if (previousKey == vKid) return; // already registered
-
 		uint previousVKid = ninKidUsed[hNin];
+		if (previousVKid == vKid) return; // already registered
 		if (previousVKid != vKid && invalidateKid == true) {
